Learning words by recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
tiny bit of conclusion

allows us to preserve most of the normative Bayesian framework within
the multi-agent setting, while avoiding paradoxes and allowing both
pragmatic reasoning and learning. The resulting model not only unifies
previous models of each phenomenon separately, it also accounts for a
range of

>>>>

If each agent in a multi-agent setting assumes the existence of a
shared, conventional norm underlying everyone's behaviour, and further
assumes that other agents are knowledgeable about this norm while they
themselves are not, then we are able to preserve most of the normative
Bayesian framework, explicitly model both learning and recursive
social reasoning simultaneously within the same framework, and avoid
paradox. The resulting theory unifies two previously separate
strands of modelling work on language usage and acquisition,
accounting for a superset of previous phenomena, while producing a
variety of new qualitative patterns. In particular, we make new
